Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-30 evaluation.tex
Added data for comparing policies.

In this section we evaluate the trade-offs of the three dropping policies
presented in Section~\ref{sec:policies.events}: unrestricted dropping, source-only
dropping, and sub-flow dropping.

@@

First, we evaluate how well the different policies are able to meet a specified
overhead budget. Figures~\ref{fig:evaluation.bc_exec_time} and
\ref{fig:evaluation.umc_exec_time} show the difference between the run-time
overheads seen and the overhead specified. These errors are averaged over all
benchmarks. A positive value means that the
overhead target was overshot while a negative value indicates that the
overheads were below the specified budget.

@@

% UMC coverage across policies
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_umc_coverage.pdf}
    \vspace{-0.2in}
    \caption{Coverage for uninitialized memory check for different dropping policies.}
    \label{fig:evaluation.umc_coverage}
    \vspace{-0.1in}
  \end{center}
\end{figure}

Next, we evaluate the coverage achieved by the different policies.
Figure~\ref{fig:evaluation.bc_coverage} shows the average coverage across
benchmarks for each of the three policies with varying overhead budgets.
Figure~\ref{fig:evaluation.umc_coverage} shows this data for uninitialized
memory check.

>>>>

% UMC coverage across policies
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_umc_coverage.pdf}
    \vspace{-0.2in}
    \caption{Coverage for uninitialized memory check for different dropping policies.}
    \label{fig:evaluation.umc_coverage}
    \vspace{-0.1in}
  \end{center}
\end{figure}
In this section we evaluate the trade-offs of unrestricted dropping and source-only dropping.
Figure~\ref{fig:evaluation.umc_exec_time} shows the difference between the
overhead budget and the run-time monitoring overheads for UMC. A positive value
means that the overhead target was overshot while a negative value indicates
that the overhead budget was met. We see similar results for unrestricted
dropping and source-only dropping due to the fact that UMC consists of a large
number of independent monitoring flows.
Figure~\ref{fig:evaluation.umc_coverage} shows the coverage of UMC for
unrestricted dropping and source-only dropping. We see that source-dropping
consistently achieves higher coverage than unrestricted dropping. This is due
to the fact that some of the overheads of monitoring for unrestricted dropping
are being spent on wasted work as discussed in Section~\ref{sec:policies.events}.

@@

@@

Next, we evaluate these trade-offs between source-only dropping and unrestricted dropping for BC.
Figure~\ref{fig:evaluation.bc_exec_time} shows the overhead differences for BC
and Figure~\ref{fig:evaluation.bc_coverage} shows the coverage for BC.
From Figure~\ref{fig:evaluation.bc_exec_time}, we see that for several
benchmarks, source-only drop fails to meet the specified overhead target.
The overshoot of the overhead target is quite high with an overhead difference
of 420\% for {\tt bzip2}, 120\% for {\tt gcc}, and 1500\% for {\tt hmmer}.
Since only array allocations are considered source events for BC, it is
difficult for source-only dropping to match overhead targets. Although
Figure~\ref{fig:evaluation.bc_coverage} again shows higher coverage for
source-only dropping, this is in part due to the fact that is running with
higher overheads.
